A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add semantic function D and its mappings

>>>>

To determine whether a formula is \textbf{True} or \textbf{False}, Burch et
al.~\cite{BURCH90} defined a structure $\mathcal{M}\left( D, I_P, I_D \right)$,
where $D$, $I_P$ and $I_D$ represent the (non-empty) \textit{domain} of
$\mathcal{M}$, the \textit{relational variable interpretation} and the
\textit{individual variable interpretation}, respectively. Furthermore, a semantic
function $\mathcal{D}$ is introduced, mapping formulas to elements of
\begin{center}
$\left( I_P \rightarrow \left( I_D \rightarrow \lbrace true, false \rbrace \right) \right)$
\end{center}
and $n$-ary relational terms to elements of
\begin{center}
$\left( I_P \rightarrow \left( I_D \rightarrow 2^{D^n} \right) \right)$
\end{center}.
